Flexibility of interactions depends on habitat suitability

### 2019-06-13 paper/manuscript.Rmd
COntinue description of species name cleaning process

@@

@@

all together we found XX instances of species that were included with a datab

>>>>

library(dplyr)

@@

```{r scientific-names-cleaning-info}
loadd(checked_sp_names, spp)

checked_sp_names <- checked_sp_names %>%
  mutate(sp_name_in_gnr = gnr_score >= 0.988, 
         sp_name_itis_invalid = itis %in% c("invalid", "not accepted"), 
         good_sp_name = sp_name_in_gnr & ! sp_name_itis_invalid, 
         # good_sp_name = if_else(is.na(good_sp_name), FALSE, good_sp_name), 
         good_queried_sp_name = good_sp_name & sp_name == queried_sp_name)

n_sp_names <- n_distinct(spp$sp_name)

n_sp_names_sp_level <- filter(spp, !sp_unidentified) %$% 
  n_distinct(sp_name)

n_sp_names_gen_level <- filter(spp, sp_unidentified, !gen_unidentified) %$% 
  n_distinct(sp_name)

n_no_tax_info <- filter(spp, gen_unidentified) %$% n_distinct(sp_name)

n_sp_correct_in_data <- checked_sp_names %>%
  filter(good_queried_sp_name) %$%
  n_distinct(queried_sp_name)

# n_sp_correct_in_data %>%
#   group_by(queried_sp_name) %>%
#   count(sort = TRUE)

# sp_incorrect_in_data <- checked_sp_names %>%
```

@@

All together, before correcting typos and synonyms, the data sources contained `r format(n_sp_names, big.mark = ",")` unique interacting species. 
Out of those, `r format(n_sp_names_sp_level, big.mark = ",")` were originally identified to the species-level, `r format(n_sp_names_gen_level, big.mark = ",")` to the genus level, and no taxonomic information was avaliable for the restant `r format(n_no_tax_info, big.mark = ",")`. 
We were able to confirm the validity of `r format(n_sp_correct_in_data, big.mark = ",")` of the scientific names of organisms identified to the species level (roughly `r scales::percent(n_sp_correct_in_data/n_sp_names_sp_level, 1)`).
